\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-08-04 forwards-and-backwards.tex
more proofs

\begin{definition}[Model parameterization and assumptions]
\label{def:model_setup}
Suppose $\gamma(x, m)$, $r(x, m)$, and $F(x, m)$
are uniformly continuous functions
from $\IR^d \times \IR_{\ge 0}$ to $\IR$.
Furthermore, suppose $r$ takes values in $[0, 1]$
and has uniformly bounded second derivatives,
that $\gamma(x,m) \ge 0$,
and that $m^2 \gamma(x, m)$ is uniformly bounded.
Fix positive values $\theta$, $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$,
with $\epsilon_r < \epsilon_\gamma$.
Suppose $F(x,m)$ is bounded above
with uniformly bounded first and second derivatives in $m$,
and define
\begin{align} \label{eqn:mu_defn}
    \mu(x, \eta)
    =
    \max\left(0, 
        r(x, \smooth{r} \eta(x))
        \gamma(\smooth{\gamma} \eta(x))
        - \frac{1}{\theta}
        F(x, \smooth{F} \eta(x)) 
    \right) .
\end{align}
Although the models will make sense without this requirement,
for the purposes of convergence we will also require that
$\theta > 2 \sup_x \sup_{y : \|y\| = 1} y^T \covq(x) y/(\epsilon_\gamma^2 - \epsilon_r^2)$.
\end{definition}

@@

\begin{lemma}
    \label{lem:eta_f_bound}
    Under the assumptions of Definition~\ref{def:model_setup},
    if $\eta^{N}_0 \to \eta_0$ weakly as $N \to \infty$,
    then for all $f \in C^2_0(\IR^d)$ there exists a $C_f < \infty$
    such that
    $$
        \IE[\langle f, \eta^N_t \rangle]
        \le
        \IE[\langle f, \eta^N_0 \rangle]
        e^{Ct}
    $$
    for all $N > 0$.
\end{lemma}

\begin{proof}
    \comment{TODO: copy over from below}
\end{proof}

@@

\begin{lemma}[Compact containment for the population process]
    \label{lem:eta_compact_containment}
    Under the assumptions of Definition~\ref{def:model_setup},
    if $\theta/N \to \alpha$ and $\eta^{N}_0 \to \eta_0$ weakly as $N \to \infty$,
    then for all $T>0$ and $N > 0$, there exists some constant $C_T$,
    such that
    \begin{align}
        \label{eqn:eta_mass_bound}
        \IE\left[
            \sup_{0 \le t \le T}
            \langle 1, \eta^{N}_t \rangle
        \right]
        \le C_T .
    \end{align}
    In particular, for any $\epsilon > 0$, there exists some $K_{\epsilon}>0$ such that
    \begin{equation}
    \limsup_{N \to \infty}
        \mathbb{P}\left[\sup_{s \in [0,T]}
            \langle 1 ,\eta^{N}_{s}\rangle
            > K_\epsilon \right]
            \leq \frac{C_T}{K_{\epsilon}} < \epsilon.    
    \end{equation}
\end{lemma}
    We first take $f \equiv 1$ in Equation \eqref{eqn:eta_martingale},
    so that
    \begin{align} \label{eqn:mass_martingale_decomp}
        \langle 1, \eta^N_t \rangle
        \langle 1, \eta^N_0 \rangle
        + \int_0^t \int_{\IR^d} \left\{
            B(x, \eta^N_s)
            + F(x, \eta^N_s)
            \right\} \eta^N_s(dx) ds
        + M^N_t(1) ,
    where $M^N_t(1)$ is a martingale and for the moment we are defining
        B(x, \eta) = \gamma(x, \eta) \int_{\IR^d} \theta (r(y, \eta) - r(x, \eta)) q_\theta(x, dy) .
    By Lemma~\ref{lem:eta_compact_containment} and the assumption that $F$ is bounded above,
    $B(x, \eta) + F(x, \eta) \le C$ for some $C$,
    and so, taking expectations,
        \IE\left[ \langle 1, \eta^N_t \rangle \right]
        &\le
        \IE\left[ \langle 1, \eta^N_0 \rangle \right]
        + C \int_0^t \IE\left[ \langle 1, \eta^N_s \rangle \right] dt .
    Applying Grownwall's inequality, we have that
        \IE\left[ \langle 1, \eta^N_t \rangle \right]
        \le
        \IE\left[ \langle 1, \eta^N_0 \rangle \right] e^{Ct} .
    Now, let $M^*_t(\phi) = \sup_{0 \le s \le t} M_t(\phi)$,
    and as before $[M(\phi)]_t$ the quadratic variation of $M_t(\phi)$,
    so that by the Burkholder-Davis-Gundy inequality, there is a $C'$ so that
        \IE\left[ M^*_t(1) \right]
        &\le
        C' \IE\left[ \sqrt{[M^*(1)]_t} \right]
        \\ &\le
        C'\left( 1 + \IE\left[ [M^*(1)]_t \right] \right)
        C'\left( 1 + \frac{\theta}{N} \IE\left[
            \int_0^t
            \int_{\IR^d} \left\{
                \gamma(x, \eta^N_s)
                \int_{\IR^d} r(y, \eta^N_s) q_\theta(x, dy)
                + \mu(x, \eta^N_s)
            \right\} \eta_s^N(dx)
            dt
            \right] \right)
        C'\left( 1 + \IE\left[
            \int_0^t
            \int_{\IR^d} \left\{
                \frac{2\theta}{N} \gamma(x, \eta^N_s) r(x, \eta^N_s)
                + \frac{1}{N} B(x, \eta^N_s)
            \right\} \eta_s^N(dx)
            dt
            \right] \right) .
    Since $\gamma(x, \eta) r(x, \eta)$ and $B(x, \eta)$ are bounded,
    and $\theta/N \to \alpha < \infty$,
    combining constants and again using Gronwall's inequality, we get that
        \IE\left[ M^*_t(1) \right]
        % &\le
        % C'\left( 1 + \IE\left[
        %     \int_0^t
        %     \int_{\IR^d} \left\{ C'' \right\} \eta_s^N(dx)
        %     dt
        %     \right] \right) \\
        &\le
        C' + C'' \IE[ \langle 1, \eta_0^N \rangle ] e^{tC} .
    Taking suprema and expectations on both sides of equation~\eqref{eqn:mass_martingale_decomp},
    then again using the fact that $B(x, \eta) + F(x, \eta) \le C$,
        \IE\left[\sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle \right]
        &\le
        \IE[\langle 1, \eta^N_0 \rangle]
        + \IE\left[
            \sup_{0 \le s \le t}
            \int_0^t \int_{\IR^d} \left\{
            B(x, \eta^N_s)
            + F(x, \eta^N_s)
            \right\} \eta^N_s(dx) ds
        \right]
        + \IE[M^*_t(1)] 
        \\
        &\le
        \IE[\langle 1, \eta^N_0 \rangle]
        + C \IE\left[
            \int_0^t \sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle ds
        \right]
        + C' + C'' \IE[ \langle 1, \eta_0^N \rangle ] e^{tC} .
    Once again applying Gronwall's inequality,
        \IE\left[\sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle \right]
        &\le
        C'' 
        \left(\IE[\langle 1, \eta^N_0 \rangle] + C'\right)
        \IE[ \langle 1, \eta_0^N \rangle ] e^{2tC} .
    For any $T$,
    the inequality on the right is bounded above by a constant $C(T)$ independent of $N$.
    As a result, for any $K > 0$,
    \limsup_{N \to \infty}
        \IP\left[ \sup_{0 \le s \le T} \langle 1, \eta^{N}_{s} \rangle \geq K \right]
        \leq
        \frac{C(T)}{K}.

@@

\begin{proof}
As in the proof of Lemma~\ref{lem:gamma_bound},
we use the semimartingale representation of $\langle f, \eta^N_t\rangle$
from Definition~\ref{defn:mgale_construction},
\begin{align*}
    \langle f, \eta^{N}_{\tau+s}\rangle
    -
    \langle f, \eta^{N}_{\tau}\rangle
    &=
    M^N_{\tau + s}(f) - M^N_\tau(f)
    +
    \int_\tau^{\tau + s} 
    \int_{\IR^d}
    \left\{
        B_f(x, \eta^N_s)
        + f(x) F(x, \eta^N_s)
    \right\} 
    \eta^N_s(dx)
    ds,
\end{align*}
where
$$
    B_f(x, \eta)
    =
    \gamma(x, \eta) \int_{\IR^d} \theta ( f(y) r(y, \eta) - f(x) r(x, \eta) ) q_\theta(x, dy) .
$$
% By Lemma~\ref{lem:gamma_bound} and the assumption that $F$ is bounded above,
% $B_f(x, \eta) + f(x) F(x, \eta) \le C_f$ for some constant $C_f$.
We apply the Aldous-Rebolledo criterion \citep{rebolledo:1980}, which says that
it suffices to show that 
$\{\langle f, \eta^N_t \rangle\}_{N \ge 1}$ is tight for each $t$, and that
for any sequence of stopping times $\tau_N$ bounded by $T$,
and for each $\epsilon > 0$, there exists $\delta > 0$ and $N_0 > 0$ such that 
\begin{gather*}
    \sup_{N > N_0}
    \sup_{s \in [0, \delta]}
    \IP\left[\left|
            \int_\tau^{\tau + s} 
            \int_{\IR^d}
            \left\{
                B_f(x, \eta^N_s)
                + f(x) F(x, \eta^N_s)
            \right\} 
            \eta^N_s(dx)
            ds
        \right|> \epsilon \right]
        < \epsilon ,
    \\ \text{and} \qquad
    \sup_{N > N_0}
    \sup_{s \in [0, \delta]}
    \IP\left[\big| [M^{N}(f)]_{\tau+s} 
                            - [M^{N}(f)]_\tau \big|
                            > \epsilon \right]
                    < \epsilon.
\end{gather*}
Tightness of $\langle f, \eta^N_t\rangle$ for fixed $t$
follows from Lemma~\ref{lem:eta_f_bound} and Markov's inequality,
so we focus on the remaining conditions.

\comment{The following is NOT RIGHT because $F$ is not bounded below!}

In particular,
\begin{multline}
 \theta\gamma(\rho_{r}*\eta^{N}_{s}(x))\int_{\mathbb{R}^n} \big\{f(y)r(\rho_{r}*\eta^{N}_{s}(y))-f(x)r(\rho_{r}*\eta^{N}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy \\
 =  f(x)\theta\gamma(\rho_{r}*\eta^{N}_{s}(x))\int_{\mathbb{R}^n} \big\{r(\rho_{r}*\eta^{N}_{s}(y))-r(\rho_{r}*\eta^{N}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy\\
 + \theta\gamma(\rho_{r}*\eta^{N}_{s}(x))\int_{\mathbb{R}^n} \big\{(f(y)-f(x))r(\rho_{r}*\eta^{N}_{s}(y))\big\}\rho_{1/\theta}(x-y)dy\\
 \leq C_{\gamma,r}||f||_{\infty} + C_{\gamma}||\Delta f||_{\infty},
\end{multline}
since the first term is bounded above by $C_{\gamma,r}f(x)$ by Lemma \ref{cor:gamma_bound}
and the second term by $C_{\gamma} \Delta f(x)$ as $r \leq 1$.

Finally,  $F(\rho_{F}*\eta^{N}_{s}(x)) f(x)$ is bounded above by $C_F||f||_{\infty}$, so 
\begin{multline}
\mathbb{E}\left[\left|
                        \langle f, \eta^{N}_{\tau+s}\rangle - \langle f, \eta^{N}_{\tau}\rangle
                \right|\right] \\
\leq (C_{\gamma,r}||f||_{\infty}
        + C_{\gamma,r}||\Delta f||_{\infty}
            +C_F||f||_{\infty})
    \mathbb{E}\bigg\{
                        \int_{\tau}^{\tau+s}
                        \bigg\langle 1,\eta^{N}_{s}(dx)  \bigg\rangle 
                        ds
                \bigg\} \\
\leq (C_{\gamma,r}||f||_{\infty}
            + C_{\gamma,r}||\Delta f||_{\infty}
                    +C_F||f||_{\infty})
                \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]
                        e^{(C_{\gamma,r}+C_F)T}(e^\delta-1).
\end{multline}
As $\eta^{N}_0$ converges weakly,
we have that 
$\sup_{\theta > \theta_0}\mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] < K$
for some $K>0$.
Applying Markov's Inequality,
we can pick small enough $\delta > 0$ such that 
\begin{equation}
\begin{aligned}
\sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\mathbb{P}\left[\left| \langle f, \eta^{N}_{\tau+s}\rangle
                        - \langle f, \eta^{N}_{\tau}\rangle
                \right|> \epsilon \right]
& \leq \sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\frac{
\mathbb{E}\left[\left| \langle f, \eta^{N}_{\tau+s}\rangle
                        - \langle f, \eta^{N}_{\tau}\rangle
                \right| \right]
        }{\epsilon}\\
& < \frac{(C_{\gamma,r}||f||_{\infty}
            + C_{\gamma,r}||\Delta f||_{\infty}
                    +C_F||f||_{\infty})
                Ke^{(C_{\gamma,r}+C_F)T}(e^\delta-1)
         }{\epsilon}\\
& < \epsilon.
\end{aligned}    
\end{equation}
Similarly, the control on the second moment is given by Equation \eqref{eq: Control quadratic variation}.
\begin{equation}
    \label{eq: Controlling Quadratic Jumps}
\begin{aligned}
& \sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}\mathbb{E}\left[\big| [M^{\theta}_{\tau+s}(f)] - [M^{\theta}_{\tau}(f)] \big|\right]\\
\leq &\frac{\theta}{N} \mathbb{E} \Bigg\{ \int_{\tau}^{\tau+s}\bigg|
\langle \gamma\big(x,\rho_{\gamma}*\eta^{N}_{s}(x)\big)
\int f^2(y)r\big(y,\rho_{r}*\eta^{N}_{s}(y)\big)q_\theta(x,dy) 
,\eta^{N}_{s}(dx)\rangle\\
& \qquad \qquad \qquad +\langle \mu\big(x,\eta^{N}_{s}\big)f^2(x) 
,\eta^{N}_{s}(dx)\rangle \bigg|ds \Bigg\}\\
\leq & \frac{2\theta}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma(\rho_{\gamma}*\eta^{N}_{s}(x))r(\rho_{r}*\eta^{N}_{s}(x)), \eta^{N}_{s}(dx) \right\rangle ds\Bigg\} \\
& + \frac{1}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma (\rho_{\gamma}*\eta^{N}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\rho_{r}*\eta^{N}_{s}(y))-r(\rho_{r}*\eta^{N}_{s}(x))\right) q_\theta(x,dy), \eta^{N}_{s}(dx) \right\rangle ds\Bigg\}\\
\leq & \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]e^{(C_{\gamma,r}+C_F)T}(e^\delta-1)}{N}.
\end{aligned}
\end{equation}
As $N^{-1}\theta \to \alpha$ as $N \to \infty$,
there exists some $K'>0$ such that 
$\sup_{\theta > \theta_0} N^{-1}\theta < K'$.
An application of Markov's inequality proves that
for small enough $\delta > 0,$
\begin{equation}
\begin{aligned}
\sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\mathbb{P}\left[\big| [M^{\theta}_{\tau+s}(f)] 
                        - [M^{\theta}_{\tau}(f)] \big|
                        > \epsilon\right]
&\leq  \sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\mathbb{E}\left[\big| [M^{\theta}_{\tau+s}(f)] 
                        - [M^{\theta}_{\tau}(f)] \big|
                        \right]/\epsilon \\
&< K'e^{(C_{\gamma,r}+C_F)T}(e^\delta-1)/\epsilon < \epsilon.
\end{aligned}    
\end{equation}
\end{proof}

\subsubsection{Tightness of $(\eta^{N}_t)_{t \geq 0}$}
\begin{theorem}
The collection of measure-valued processes 
$\{(\eta^{N}_t)_{t \geq 0}: \theta > 0\}$
is tight in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_F(\overline{\mathbb{R}^d}))$.
\end{theorem}
\begin{proof}
To prove relative compactness 
of the processes $(\eta^{N}_t)_{t \geq 0}$,
we apply Theorem 3.9.1. in \cite{EK}.

>>>>

\begin{definition}[Model parameterization and assumptions]
\label{def:model_setup}
Suppose $\gamma(x, m)$, $r(x, m)$, and $F(x, m)$
are uniformly continuous functions
from $\IR^d \times \IR_{\ge 0}$ to $\IR$.
Furthermore, suppose $r$ takes values in $[0, 1]$
and has uniformly bounded second derivatives,
that $\gamma(x,m) \ge 0$,
and that $m^2 \gamma(x, m)$ is uniformly bounded.
Fix positive values $\theta$, $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$,
with $\epsilon_r < \epsilon_\gamma$.
Suppose $F(x,m)$ is bounded above
with uniformly bounded first and second derivatives in $m$,
that $\sup_x F(x,m)$ is finite for all $m$,
and define
\begin{align} \label{eqn:mu_defn}
    \mu(x, \eta)
    =
    \max\left(0, 
        r(x, \smooth{r} \eta(x))
        \gamma(\smooth{\gamma} \eta(x))
        - \frac{1}{\theta}
        F(x, \smooth{F} \eta(x)) 
    \right) .
\end{align}
Although the models will make sense without this requirement,
for the purposes of convergence we will also require that
$\theta > 2 \sup_x \sup_{y : \|y\| = 1} y^T \covq(x) y/(\epsilon_\gamma^2 - \epsilon_r^2)$.
\end{definition}

@@

\begin{lemma}
    \label{lem:eta_f_bound}
    Under the assumptions of Definition~\ref{def:model_setup},
    if $\eta^{N}_0 \to \eta_0$ weakly as $N \to \infty$,
    then for all $f \in C^2_0(\IR^d)$ there exists a $C_f < \infty$
    such that
    $$
        \IE[\langle f, \eta^N_t \rangle]
        \le
        \IE[\langle f, \eta^N_0 \rangle]
        e^{C_f t}
    $$
    for all $N > 0$.
\end{lemma}

\begin{proof}
    Consider the semimartingale decomposition of Equation \eqref{eqn:eta_martingale},
    \begin{align} \label{eqn:eta_f_mgale_decomp}
        \langle f, \eta^N_t \rangle
        &=
        \langle f, \eta^N_0 \rangle
        + \int_0^t \int_{\IR^d} \left\{
            \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
            + f(x) F(x, \eta^N_s)
            \right\} \eta^N_s(dx) ds
        + M^N_t(f) ,
    \end{align}
    where $M^N_t(f)$ is a martingale and for the moment we are defining
    \begin{equation*}
        B_f(x, \eta) = \int_{\IR^d} \theta (f(y) r(y, \eta) - f(x) r(x, \eta)) q_\theta(x, dy) .
    \end{equation*}
    By Lemma~\ref{lem:eta_compact_containment} and the assumption that $F$ is bounded above,
    $\gamma(x, \eta) B_f(x, \eta) + f(x) F(x, \eta) \le C_f$ for some $C_f$,
    and so, taking expectations,
    \begin{align*}
        \IE\left[ \langle f, \eta^N_t \rangle \right]
        &\le
        \IE\left[ \langle f, \eta^N_0 \rangle \right]
        + C_f \int_0^t \IE\left[ \langle f, \eta^N_s \rangle \right] dt .
    \end{align*}
    The bound then follows from Grownwall's inequality.
\end{proof}

@@

\begin{lemma}[Compact containment for the population process]
    \label{lem:eta_compact_containment}
    Under the assumptions of Definition~\ref{def:model_setup},
    if $\theta/N \to \alpha$ and $\eta^{N}_0 \to \eta_0$ weakly as $N \to \infty$,
    then for all $T>0$ and $N > 0$, there exists some constant $C_T$,
    such that
    \begin{align}
        \label{eqn:eta_mass_bound}
        \IE\left[
            \sup_{0 \le t \le T}
            \langle 1, \eta^{N}_t \rangle
        \right]
        \le C_T .
    \end{align}
    In particular, for any $\epsilon > 0$, there exists some $K_{\epsilon}>0$ such that
    \begin{equation}
    \limsup_{N \to \infty}
        \IP \left\{ \sup_{s \in [0,T]}
            \langle 1 ,\eta^{N}_{s}\rangle
            > K_\epsilon \right\}
        \leq \frac{C_T}{K_{\epsilon}}
        < \epsilon .
    \end{equation}
\end{lemma}

\begin{proof}
    First note that by Lemma~\ref{lem:eta_f_bound},
    $\IE[\langle 1, \eta^N_t \rangle] \le \IE[\langle 1, \eta^N_0 \rangle] e^{Ct}$
    for some $C$.
    Now, let $M^*_t(f) = \sup_{0 \le s \le t} M_t(f)$,
    and as before $[M(f)]_t$ the quadratic variation of $M_t(f)$,
    so that by the Burkholder-Davis-Gundy inequality, there is a $C'$ so that
    \begin{align*}
        \IE\left[ M^*_t(1) \right]
        &\le
        C' \IE\left[ \sqrt{[M^*(1)]_t} \right]
        \\ &\le
        C'\left( 1 + \IE\left[ [M^*(1)]_t \right] \right)
        \\ &=
        C'\left( 1 + \frac{\theta}{N} \IE\left[
            \int_0^t
            \int_{\IR^d} \left\{
                \gamma(x, \eta^N_s)
                \int_{\IR^d} r(y, \eta^N_s) q_\theta(x, dy)
                + \mu(x, \eta^N_s)
            \right\} \eta_s^N(dx)
            dt
            \right] \right)
        \\ &=
        C'\left( 1 + \IE\left[
            \int_0^t
            \int_{\IR^d} \left\{
                \frac{2\theta}{N} \gamma(x, \eta^N_s) r(x, \eta^N_s)
                + \frac{1}{N} B(x, \eta^N_s)
            \right\} \eta_s^N(dx)
            dt
            \right] \right) .
    \end{align*}
    Since $\gamma(x, \eta) r(x, \eta)$ and $B(x, \eta)$ are bounded,
    and $\theta/N \to \alpha < \infty$,
    combining constants and again using Gronwall's inequality, we get that
    \begin{align*}
        \IE\left[ M^*_t(1) \right]
        % &\le
        % C'\left( 1 + \IE\left[
        %     \int_0^t
        %     \int_{\IR^d} \left\{ C'' \right\} \eta_s^N(dx)
        %     dt
        %     \right] \right) \\
        &\le
        C' + C'' \IE[ \langle 1, \eta_0^N \rangle ] e^{tC} .
    \end{align*}
    Taking suprema and expectations on both sides of equation~\eqref{eqn:eta_f_mgale_decomp},
    then again using the fact that $\gamma(x, \eta) B(x, \eta) + F(x, \eta) \le C$,
    \begin{align*}
        \IE\left[\sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle \right]
        &\le
        \IE[\langle 1, \eta^N_0 \rangle]
        + \IE\left[
            \sup_{0 \le s \le t}
            \int_0^t \int_{\IR^d} \left\{
                \gamma(x, \eta^N_s)
                B(x, \eta^N_s)
                + F(x, \eta^N_s)
            \right\} \eta^N_s(dx) ds
        \right]
        + \IE[M^*_t(1)] 
        \\
        &\le
        \IE[\langle 1, \eta^N_0 \rangle]
        + C \IE\left[
            \int_0^t \sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle ds
        \right]
        + C' + C'' \IE[ \langle 1, \eta_0^N \rangle ] e^{tC} .
    \end{align*}
    Once again applying Gronwall's inequality,
    \begin{align*}
        \IE\left[\sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle \right]
        &\le
        C'' 
        \left(\IE[\langle 1, \eta^N_0 \rangle] + C'\right)
        \IE[ \langle 1, \eta_0^N \rangle ] e^{2tC} .
    \end{align*}
    For any $T$,
    the inequality on the right is bounded above by a constant $C(T)$ independent of $N$.
    As a result, for any $K > 0$,
    \begin{equation*}
    \limsup_{N \to \infty}
        \IP\left[ \sup_{0 \le s \le T} \langle 1, \eta^{N}_{s} \rangle \geq K \right]
        \leq
        \frac{C(T)}{K}.
    \end{equation*}
\end{proof}

\begin{lemma}
    \label{lem:tightness_for_F}
    Fix a $\sigma > 0$ and a continuous function $f \in C(\IR^d, [0, \infty))$
    such that $\sup_x f(x, m)$ is finite for each $m$.
    Under the assumptions of Definition~\ref{def:model_setup},
    and if $\eta^N_0$ converges in distribution,
    for all $\epsilon > 0$ and $T \ge 0$
    there exists a $K_f$ such that for all $N > 0$,
    \begin{align*}
        \IP\left\{
            \sup_{0 \le s \le T}
            \int_{\IR^d}
            f(x, p_{\sigma^2}*\eta^N_s(x))
            \eta^N_s(dx)
            > K_f
        \right\}
        \le \epsilon ,
    \end{align*}
    where recall that $p_{\sigma^2}*\eta(\cdot)$ denotes convolution of the Gaussian kernel
    with mean 0 and variance $\sigma^2 I$ with the measure $\eta$.
\end{lemma}

\begin{proof}[of Lemma~\ref{lem:tightness_for_F}]
    Let $\bar f(m) = \sup_x \sup_{k \le m} f(x, k)$, which is finite by assumption.
    Since $p_{\sigma^2}*\eta(x) \le \langle 1, \eta \rangle / (2 \pi \sigma^2)^{d/2}$,
    we have that
    $$
        \sup_{0 \le s \le T} \sup_{x \in \IR^d} f(x, p_{\sigma^2}*\eta^N_s(x))
        \le
        \bar f( \sup_{0 \le s \le T} \langle 1, \eta^N_s \rangle  / (2 \pi \sigma^2)^{d/2} ) .
    $$
    This implies that if $0 \le s \le T$ then
    $$
            \int_{\IR^d} f(x, p_{\sigma^2}*\eta^N_s(x)) \eta^N_s(dx)
            \le
            \bar f(\sup_{0 \le s \le T} \langle 1, \eta^N_s \rangle)
            \sup_{0 \le s \le T} \langle 1, \eta^N_s \rangle .
    $$
    Now, if we let $g(m) = m \bar f(m/ (2 \pi \sigma^2)^{d/2})$,
    which again is finite and nondecreasing,
    then the lemma follows by choosing $K_f = g^{-1}(K_\epsilon)$
    in Lemma~\ref{lem:eta_compact_containment}.
\end{proof}

@@

\begin{proof}
We apply the Aldous-Rebolledo criterion \citep{rebolledo:1980}, which 
applied to the semimartingale representation of $\langle f, \eta^N_t\rangle$
of equation~\eqref{eqn:eta_f_mgale_decomp},
says that it suffices to show that 
$\{\langle f, \eta^N_t \rangle\}_{N \ge 1}$ is tight for each $t$, and that
for any sequence of stopping times $\tau_N$ bounded by $T$,
and for each $\epsilon > 0$, there exists $\delta > 0$ and $N_0 > 0$ such that 
\begin{gather}
        \label{eqn:eta_projections_goal1}
    \sup_{N > N_0}
    \sup_{t \in [0, \delta]}
    \IP\left\{\left|
            \int_\tau^{\tau + t}
            \int_{\IR^d}
            \left\{
                \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
                + f(x) F(x, \eta^N_s)
            \right\} 
            \eta^N_s(dx)
            ds
        \right|> \epsilon \right\}
        < \epsilon ,
    \\ \text{and} \qquad
        \label{eqn:eta_projections_goal2}
    \sup_{N > N_0}
    \sup_{t \in [0, \delta]}
    \IP\left\{\big|
        [M^{N}(f)]_{\tau + t} 
            - [M^{N}(f)]_\tau \big|
        > \epsilon
    \right\}
    < \epsilon.
\end{gather}
Tightness of $\langle f, \eta^N_t\rangle$ for fixed $t$
follows from Lemma~\ref{lem:eta_f_bound} and Markov's inequality,
so we focus on the remaining conditions.

Next, note that for $0 \le t \le \delta$,
if we choose $K_f$ as in Lemma~\ref{lem:tightness_for_F}
and $C_f$ as in Lemma~\ref{lem:gamma_bound},
then
\begin{align*}
    &
    \IP\left\{
        \int_\tau^{\tau + t}
        \int_{\IR^d}
        \left\{
            \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
            + f(x) F(x, \eta^N_s)
        \right\} 
        \eta^N_s(dx)
        ds
        > (K_f + C_f) \delta
    \right\}
    \\ & \qquad \le
    \IP\left\{
        \sup_{0 \le s \le \delta}
        \int_{\IR^d} \left\{
            \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
            + f(x) F(x, \eta^N_s)
        \right\} \eta^N_s(dx)
        >
        K_f + C_f
    \right\}
    < \epsilon .
\end{align*}
Therefore, setting $\delta = \epsilon / (K_f + C_f)$
obtains \eqref{eqn:eta_projections_goal1}.

Similarly,
\begin{align*}
    &
    [M^{N}(f)]_{\tau + t} 
        - [M^{N}(f)]_\tau \big|
    \\ & \qquad =
    \int_{\tau}^{\tau + t}
        \frac{\theta}{N}
        \int_{\IR^d}
        \left\{
            \gamma(x, \eta^N_s)
            \int_{\IR^d} f^2(y) r(y, \eta^N_s) q_\theta(x, dy)
            +
            \mu(x, \eta^N_s) f^2(x)
        \right\}
        \eta^N_s(dx)
    ds .
    \\ & \qquad =
    \int_{\tau}^{\tau + t}
        \frac{\theta}{N}
        \int_{\IR^d}
        \left\{
            \gamma(x, \eta^N_s)
            \left(
                2 f^2(x) r(x, \eta^N_s)
                +
                B_{f^2}(x, \eta^N_s)
            \right)
            +
            f^2(x) F(x, \eta^N_s) / \theta
        \right\}
        \eta^N_s(dx)
    ds ,
\end{align*}
and so using the fact that $\theta/N \to \alpha < \infty$,
an argument similar to 
that for \eqref{eqn:eta_projections_goal1}.
also obtains \eqref{eqn:eta_projections_goal2}.

% % % % % % % % %
\begin{theorem}[Tightness of $(\eta^{N}_t)_{t \geq 0}$]
The collection of measure-valued processes 
$\{(\eta^{N}_t)_{t \geq 0}: \theta > 0\}$
is tight in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_F(\overline{\mathbb{R}^d}))$.
\end{theorem}
\begin{proof}
To prove relative compactness 
of the processes $(\eta^{N}_t)_{t \geq 0}$,
we apply Theorem 3.9.1. in \cite{EK}.
